The one characterizing the parental care stages

### 2019-10-11 docs/ms1-charactization.Rmd
now with hormone characterization data
three sets of hormone figs
now with timeline
more figs

![](../figures/images/PigeonHPGaxis.png)

![](../figures/images/samplingtimepoints.png)

@@

>>>>

### Fig 1: graphical abstract of methods

![](../figures/images/timeline_timeline.png)

@@

## Fig 2: circulating prolactin peaks at hatch in M and F

![](../figures/hormones/characterization-1.png)

### Fig 2 supplement. CORT but not E,T, or P respond significantly to treatment

![](../figures/hormones/characterization-2.png)

## Figure 3: general rnaseq pattern, tissue > sex > stage

_Needs to be replaced with a better PCA plot_

![](../figures/limma/plotMDS-colored-1.png)

## Figure 4: model showing ability to predict non-parental, egg care, and nestingling care

![](../figures/characterization/DoveParentsRNAseq_model2.png)

## Figure 5: PRL in prolatin mirrors PRL in bloo

![](../figures/characterization/prolactin-1.png)

## Figure 6: many genes mirror the PRL expression pattern

![](../figures/sexes/wgcna2-1.png)
